---
title: "World Military Expenditures"
author: "Ethan Tenison"
date: "7/21/2019"
output: html_document
---

```{r libraries}
library(dplyr)
library(cartogram) 
library(mapproj)
library(maptools)
library(tidyverse)
library(broom)
library(viridis)

```

The data I used is from the SIPRI Military Expenditure Database. 
```{r adding military expenditure data}

military_expenditure <- read.csv("Military_expenditure_iso2.csv")

military_expenditure <- rename(military_expenditure, ISO2 = ï..ISO2,expenditure_2018 = X2018)

```


Wrld_simpl is a "Large SpatialPolygonDataFrame". In the Africa example, when afr is created the data frame is converted to a "Formal Class SpatialPolygonDataFrame", but that is not the case here where I have selected Asia. The dataframe remains the same class. 
```{r joining the two together}
data(wrld_simpl)

asia=wrld_simpl[wrld_simpl$REGION==142,]

asia@data <- left_join(asia@data, military_expenditure, by = "ISO2")

asia@data$expenditure_2018 <- as.double(asia@data$expenditure_2018)

asia@data$expenditure_2018[is.na(asia@data$expenditure_2018)] <- 1
```


```{r cartogram, cache= TRUE}
asia_cartogram <- cartogram_cont(asia, "expenditure_2018", itermax=30)
```


When the data is transformed using tidy(), the ISO3 informatino disappers. This does not happen in the Africa example. 
```{r ggplÓt}
spdf_fortified <- tidy(asia_cartogram)
spdf_fortified = spdf_fortified %>% left_join(. , asia_cartogram@data, by=c("id"="ISO3")) 

```


``` {r plÓt}
ggplot() +
  geom_polygon(data = spdf_fortified, aes(fill = expenditure_2018, x = long, y = lat, group = group) , size=0, alpha=0.9) +
  coord_map() +
  theme_void()
```